---
title: "The Impact of COVID-19 on Mental Health in the US (Group Assignment)"
author: "Chaoran Yang, Yinxi Jiang, Zhilong Shang, Xiaolu Luo, Qifan Zhang"
date: "2026-01-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
# Importing libraries
packages = (c("ipumsr", "dplyr", "ggplot2", "tidyr","gtsummary","here", "rmdformats", "srvyr","knitr","kableExtra", "survey", "scales","marginaleffects", "fixest", "modelsummary"))

package.check <- lapply(
  packages,
  FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  }
)
```

# Loading data

```{r}
ddi <- read_ipums_ddi("nhis_00006.xml")
data <- read_ipums_micro(ddi)
head(data)
```

```{r}
ipums_val_labels(data$SEX)
```

# Data cleaning & wrangling

```{r}
# Choosing analysis sample: adults in year 2017-19, 2021-2022
filtered_data <- data %>%
  filter(YEAR != 2020 & AGE >= 18 & AGE <= 99) %>%
  mutate(
    # Encoding: Pandemic era difining: 2017-19 as Baseline, 2021-22 as Pandemic Era
    Pandemic_Era = case_when(
      YEAR %in% c(2017, 2018, 2019) ~ "Pre_Pandemic (2017-19)",
      YEAR %in% c(2021, 2022) ~ "Pandemic (2021-22)",
      TRUE ~ NA_character_
    ),
    
    Pandemic_Era = factor(Pandemic_Era, 
                          levels = c("Pre_Pandemic (2017-19)", "Pandemic (2021-22)")),
    
    # Recode Outcomes: Define "High Frequency" as Daily(1) or Weekly(2)
    High_Anxiety = case_when(
      WORFREQ %in% c(1, 2) ~ 1,
      WORFREQ %in% c(3, 4, 5) ~ 0,
      TRUE ~ NA_real_
    ),
    
    High_Depression = case_when(
      DEPFREQ %in% c(1, 2) ~ 1,
      DEPFREQ %in% c(3 ,4, 5) ~ 0,
      TRUE ~ NA_real_
    ),
    
    # Recode SES Control (Education): Grouped into 4 standard categories
    # Note: EDUC is treated as a pre-determined baseline SES
    Education_levels = case_when(
      EDUC < 200 ~ "Less than HS",
      EDUC >= 200 & EDUC < 300 ~ "High School",
      EDUC >= 300 & EDUC < 400 ~ "Some College",
      EDUC >= 400 & EDUC < 900 ~ "Bachelor or Higher",
      TRUE ~ NA_character_
    ),
    # Setting education level order
    Education_levels = factor(Education_levels,
                             level = c("Less than HS", "High School", "Some College", "Bachelor or Higher")),
    
    # # Recode Economic Mechanism (SNAP): Treated as time-varying economic shock
    Received_SNAP = case_when(
      GOTSTAMPFAM %in% c(20, 21, 22) ~ "Yes",
      GOTSTAMPFAM == 10 ~ "No",
      TRUE ~ NA_character_
    ),
    
    # Encoding: Race
    Race_Ethnicity = case_when(
      RACENEW == 100 ~ "White",
      RACENEW == 200 ~ "Black",
      RACENEW == 400 ~ "Asian",
      RACENEW %in% c(300, 500, 510, 520, 530, 540, 541, 542) ~ "Other/Multiple",
      RACENEW >= 900 ~ NA_character_, 
      TRUE ~ NA_character_
    ),
    Race_Ethnicity = factor(Race_Ethnicity, 
                            levels = c("White", "Black", "Asian", "Other/Multiple"))
  ) %>%
  # Drop missing values to ensure Complete Case Analysis for regression models
  drop_na(Pandemic_Era, High_Anxiety, Education_levels, Received_SNAP, Race_Ethnicity, High_Depression)

# Cheacking for data vloume
print(paste("Row_data sample size:", nrow(data)))
print(paste("Filtered_data sample size:", nrow(filtered_data)))
table(filtered_data$Pandemic_Era)

```

# EDA

NOTE: All prevalence rates in charts are WEIGHTED using 'SAMPWEIGHT' to represent the US adult population, except for the sample balance plot.

```{r}
# Setting consistent theme
my_theme <-theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "#2c3e50"),
    plot.subtitle = element_text(color = "#7f8c8d"),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```

## Sample balance

```{r}
# Checking data volume by year
sample_balance <- filtered_data %>%
  group_by(YEAR) %>%
  summarise(Count = n()) %>%
  ggplot(aes(x = factor(YEAR), y = Count)) + 
  geom_col(fill = "#E46AA3", width = 0.3, alpha = 0.9) + 
  geom_text(aes(label = scales::comma(Count)), vjust = -0.3, size = 4) +
  labs(
    title = "Sample Distribution by Survey Year",
    subtitle = "Number of adult respondent (Age 18+) after filtering",
    x = "Survey Year",
    y = "Number of Respondents"
  ) + 
  scale_y_continuous(labels = scales::comma) + 
  my_theme

print(sample_balance)
```

## Weighted Descriptive Statistics

```{r}
# --- Table: Weighted Descriptive Statistics (Demographics) ---

# Data Preparation: Select variables and factorize SEX
table_data <- filtered_data %>%
  select(
    Pandemic_Era, 
    SEX, 
    Race_Ethnicity, 
    Education_levels, 
    Received_SNAP, 
    SAMPWEIGHT
  ) %>%
  mutate(
    # Convert raw SEX codes to labeled factor
    SEX = factor(SEX, levels = c(1, 2), labels = c("Male", "Female"))
  )

# Define Survey Design
des_table <- svydesign(ids = ~1, weights = ~SAMPWEIGHT, data = table_data)

# Generate Weighted Summary Table
table1 <- des_table %>%
  tbl_svysummary(
    by = Pandemic_Era, 
    include = c(SEX, Race_Ethnicity, Education_levels, Received_SNAP),
    
    # Display weighted percentages only (cleaner look)
    statistic = list(all_categorical() ~ "{p}%"), 
    
    # Keep 1 decimal place
    digits = list(all_categorical() ~ 1),
    
    # Custom labels
    label = list(
      SEX ~ "Gender",
      Race_Ethnicity ~ "Race / Ethnicity",
      Education_levels ~ "Education Level",
      Received_SNAP ~ "Received SNAP (Family)"
    ),
    missing = "no"
  ) %>%
  add_overall() %>% 
  modify_header(label = "**Characteristic**") %>% 
  bold_labels() %>% 
  modify_caption("**Table. Weighted Characteristics of Study Population (2017-2022)**")

# Print Table (Converted to flex_table for font sizing)
# Note: Using as_flex_table allows resizing if the table is too large
library(flextable) 
table1 %>%
  as_flex_table() %>%
  fontsize(size = 9) %>%
  autofit()                # Auto-adjust column widths
```

## Main trend of anxiety

```{r}
# --- Figure: Main Trend of Anxiety (Weighted) ---
# Visualizing the aggregate change in anxiety prevalence before and during the pandemic
Anxiety_Rate <- filtered_data %>%
  group_by(Pandemic_Era) %>%
  summarise(
    # Calculate weighted mean using survey weights (SAMPWEIGHT) to represent US population
    Anxiety_Rate = weighted.mean(High_Anxiety, SAMPWEIGHT, na.rm = TRUE),
    # Calculate approximate standard error for error bars
    se = sd(High_Anxiety, na.rm = TRUE) / sqrt(n()) 
  ) %>%
  ggplot(aes(x = Pandemic_Era, y = Anxiety_Rate, fill = Pandemic_Era)) +
  geom_col(width = 0.3, show.legend = FALSE) +
  # Add 95% Confidence Intervals (1.96 * SE)
  geom_errorbar(aes(ymin = Anxiety_Rate - 1.96*se, ymax = Anxiety_Rate + 1.96*se), 
                width = 0.1, color = "#2c3e50") +
  # Add percentage labels above bars
  geom_text(aes(label = scales::percent(Anxiety_Rate, accuracy = 0.1)), 
            vjust = -0.45, fontface = "bold") +
  # Custom colors: Green for Pre-Pandemic, Pink for Pandemic
  scale_fill_manual(values = c("#2CA25F", "#E46AA3")) + 
  scale_y_continuous(labels = scales::percent_format()) + 
  labs(
    title = "Rise in Frequent Anxiety Symptoms During the Pandemic",
    subtitle = "Weighted proportion of US adults reporting daily or weekly anxiety", 
    x = NULL,
    y = "Prevalence Rate (Weighted)"
  ) +
  my_theme

print(Anxiety_Rate)
```

## Socio-economic status heterogeneity

```{r}
# --- Figure: Socio-economic Status Heterogeneity ---
# Analyzing how anxiety trends differ across educational groups (SES proxy)
Status_graph <- filtered_data %>%
  # Group by both time period and education to observe interaction effects
  group_by(Pandemic_Era, Education_levels) %>%
  summarise(
      # Calculate weighted prevalence to ensure representativeness within each education group
      Anxiety_Rate = weighted.mean(High_Anxiety, SAMPWEIGHT, na.rm = TRUE), 
      .groups = "drop"
  ) %>%
  ggplot(aes(x = Education_levels, y = Anxiety_Rate, fill = Pandemic_Era)) +
  geom_col(position = "dodge", alpha = 0.9) +
  scale_fill_manual(values = c("#2CA25F", "#E46AA3"), name = "Time Period") +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Anxiety Trends by Educational Attainment",
    subtitle = "Weighted comparison across socioeconomic groups",
    x = NULL,
    y = "Prevalence of High Anxiety"
  ) +
  my_theme +
  # Prevent text overlap for long education categories
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 0.8)
        )

print(Status_graph)
```

## Anxiety Faceted Heatmap

```{r}
# --- Figure: Anxiety Faceted Heatmap ---
# Exploring the interaction between Age and Education on anxiety risk
heatmap_data <- filtered_data %>%
  # Create discrete Age Groups to analyze life-stage differences (Young vs. Old)
  mutate(Age_Group = cut(AGE, 
                         breaks = c(17, 29, 44, 64, 85), 
                         labels = c("18-29", "30-44", "45-64", "65+"))) %>%
  # Group by three dimensions to calculate specific cell values for the heatmap
  group_by(Pandemic_Era, Education_levels, Age_Group) %>%
  summarise(
      # Apply weights
      Anxiety_Rate = weighted.mean(High_Anxiety, SAMPWEIGHT, na.rm = TRUE), 
      .groups = "drop"
  )

p_heatmap <- ggplot(heatmap_data %>% filter(!is.na(Age_Group)), aes(x = Age_Group, y = Education_levels, fill = Anxiety_Rate)) +
  geom_tile(color = "white", size = 0.5) + 
  # Create side-by-side panels to visualize the shift in "risk hotspots" over time
  facet_wrap(~Pandemic_Era) +
  # 'PiYG' palette: Green = Low Anxiety, Pink/Purple = High Anxiety
  scale_fill_distiller(palette = "PiYG", direction = -1, labels = scales::percent) +
  geom_text(aes(label = scales::percent(Anxiety_Rate, accuracy = 1)), color = "black", size = 3) +
  labs(
    title = "Heatmap of Anxiety Risk: Age vs. Education",
    subtitle = "Comparing weighted risk hotspots before and during the pandemic",
    x = "Age Group",
    y = "Education Level",
    fill = "Anxiety Rate"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    panel.grid = element_blank(), 
    axis.text.x = element_text(angle = 0),
    legend.position = "right"
  )

print(p_heatmap)
```

## The Age Curve of Mental Health

```{r}
# --- Figure: Age Curve of Mental Health (Smoothed Trend) ---
# Visualizing the continuous relationship between Age and Anxiety Probability
p_trend <- ggplot(filtered_data, 
                  aes(x = AGE, y = High_Anxiety, 
                      color = Pandemic_Era, fill = Pandemic_Era, 
                      weight = SAMPWEIGHT)) +

  # Use Generalized Additive Model (GAM) for smoothing
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), alpha = 0.2) + 
  
  scale_color_manual(values = c("#2CA25F", "#E46AA3")) + 
  scale_fill_manual(values = c("#2CA25F", "#E46AA3")) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "The 'Youth Crisis': Anxiety Trends Across Age",
    subtitle = "Weighted smoothed probability of high anxiety by age (with 95% CI)",
    x = "Age (Years)",
    y = "Probability of High Anxiety",
    color = "Time Period",
    fill = "Time Period"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "top")

print(p_trend)
```

## Trends in Frequent Depressive Symptoms Among U.S. Adults

```{r}
# --- Figure: Depression Trends Over Time (2017-2022) ---
# Objective: Visualize the trajectory of depression prevalence and check for pre-trends.

COL_PRE  <- "#2CA25F"
COL_POST <- "#E46AA3"

trend_depression <- filtered_data %>%
  group_by(YEAR) %>%
  summarise(
    Depression_Rate = weighted.mean(High_Depression, SAMPWEIGHT, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Era = ifelse(YEAR <= 2019, "Pre", "Pandemic"),
    Era = factor(Era, levels = c("Pre", "Pandemic"))
  )

ggplot(trend_depression, aes(x = YEAR, y = Depression_Rate)) +
  geom_line(linewidth = 1, color = "black") +
  # Add points colored by Era to highlight the structural break
  geom_point(aes(color = Era), size = 2.5) +
  scale_color_manual(values = c("Pre" = COL_PRE, "Pandemic" = COL_POST), name = "Time Period") +
  scale_y_continuous(labels = percent_format(accuracy = 0.1)) +
  # Explicitly set x-axis breaks to show the gap for the excluded year (2020)
  scale_x_continuous(breaks = c(2017, 2018, 2019, 2021, 2022)) +
  labs(
    title = "Trends in Frequent Depressive Symptoms Among U.S. Adults, 2017–2022",
    subtitle = "Weighted prevalence of adults reporting daily/weekly depression (Age 18+)",
    x = "Survey Year",
    y = "Prevalence of High Depression"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(color = "grey40", size = 10),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )

print(trend_depression)

```

## Frequent Anxiety Symptoms by Household SNAP Receip

```{r}
# --- Figure: Economic Mechanism Check (SNAP vs. Depression) ---
# Initialize Survey Design
des <- svydesign(ids = ~1, weights = ~SAMPWEIGHT, data = filtered_data)

# Calculate Weighted Statistics
snap_depression_w <- svyby(
  ~High_Depression,
  ~Pandemic_Era + Received_SNAP,
  des,
  svymean,
  na.rm = TRUE,
  vartype = c("se")
) %>%
  as.data.frame() %>%
  rename(Depression_Rate = High_Depression, se = se) %>%
  mutate(
    # Setting factor order
    Pandemic_Era = factor(Pandemic_Era,
                          levels = c("Pre_Pandemic (2017-19)", "Pandemic (2021-22)")),
    Received_SNAP = factor(Received_SNAP, levels = c("No", "Yes")),
    # Calculate 95% Confidence Intervals for error bars
    lo = Depression_Rate - 1.96 * se,
    hi = Depression_Rate + 1.96 * se
  )

ggplot(snap_depression_w, aes(x = Received_SNAP, y = Depression_Rate, fill = Pandemic_Era)) +
  # Side-by-side bars to compare time periods within each SNAP category
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  # Add error bars
  geom_errorbar(aes(ymin = lo, ymax = hi),
                position = position_dodge(width = 0.8),
                width = 0.15, linewidth = 0.6) +
  geom_text(aes(label = percent(Depression_Rate, accuracy = 0.1)),
            position = position_dodge(width = 0.8),
            vjust = -0.35, size = 4) +
  scale_fill_manual(values = c("Pre_Pandemic (2017-19)" = COL_PRE,
                               "Pandemic (2021-22)" = COL_POST),
                    name = "Time Period") +
  scale_y_continuous(labels = percent_format(), limits = c(0, NA)) +
  labs(
    title = "Frequent Depression by SNAP Receipt (Weighted): Pre vs Pandemic",
    subtitle = "NHIS sample adult weights; 95% confidence intervals shown",
    x = "Household Received SNAP",
    y = "Prevalence of High Depression"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(color = "grey40", size = 11),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```

## Mental Health Differences by SES Type: Education (Pre-determined) vs SNAP (Time-varying)

```{r}
# --- Figure: Mental Health Differences by SES Type (Faceted) ---
ses_long <- filtered_data %>%
  select(Pandemic_Era, High_Anxiety, Education_levels, Received_SNAP) %>%
  pivot_longer(
    cols = c(Education_levels, Received_SNAP),
    names_to = "SES_Type",
    values_to = "SES_Group"
  ) %>%
  mutate(
    Pandemic_Era = factor(Pandemic_Era, levels = c("Pre_Pandemic (2017-19)", "Pandemic (2021-22)")),
    SES_Type = factor(SES_Type, levels = c("Education_levels", "Received_SNAP"), labels = c("Education", "SNAP"))
  ) %>%
  # Calculate WEIGHTED means before plotting
  group_by(Pandemic_Era, SES_Type, SES_Group) %>%
  summarise(
    Anxiety_Rate = weighted.mean(High_Anxiety, filtered_data$SAMPWEIGHT[1:n()], na.rm = TRUE), 
    .groups = "drop"
  )

ggplot(ses_long, aes(x = SES_Group, y = Anxiety_Rate, fill = Pandemic_Era)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  facet_wrap(~ SES_Type, scales = "free_x") +
  scale_fill_manual(
    values = c("Pre_Pandemic (2017-19)" = COL_PRE, "Pandemic (2021-22)" = COL_POST),
    name = "Time Period"
  ) +
  scale_y_continuous(labels = percent_format()) +
  labs(
    title = "Mental Health Differences by SES Type",
    subtitle = "Weighted prevalence of high anxiety: Education (pre-determined) vs SNAP (time-varying)",
    x = NULL,
    y = "Prevalence of High Anxiety"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 18),
    plot.subtitle = element_text(color = "grey40", size = 13),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    # Rotate x-axis text to prevent overlap
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

## Gender Differences in Anxiety Symptoms, Pre vs During Pandemic

```{r}
# --- Figure: Gender Differences in Anxiety (Weighted) ---
COL_PRE  <- "#2CA25F"
COL_POST <- "#E46AA3"

filtered_data <- filtered_data %>%
  mutate(Gender = factor(SEX, levels = c(1, 2), labels = c("Male", "Female")))


# Define survey object using 'SAMPWEIGHT'
des <- svydesign(ids = ~1, weights = ~SAMPWEIGHT, data = filtered_data)

# Compute weighted prevalence and standard errors for each Gender-Era combination
gender_anxiety_w <- svyby(
  ~High_Anxiety,
  ~Pandemic_Era + Gender,
  des,
  svymean,
  na.rm = TRUE,
  vartype = "se"
) %>%
  as.data.frame() %>%
  rename(Anxiety_Rate = High_Anxiety, se = se) %>%
  mutate(
    Pandemic_Era = factor(Pandemic_Era,
                          levels = c("Pre_Pandemic (2017-19)", "Pandemic (2021-22)")),
    Gender = factor(Gender, levels = c("Male", "Female")),
    lo = Anxiety_Rate - 1.96 * se,
    hi = Anxiety_Rate + 1.96 * se
  )

ggplot(gender_anxiety_w, aes(x = Gender, y = Anxiety_Rate, fill = Pandemic_Era)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  # Add error bars
  geom_errorbar(aes(ymin = lo, ymax = hi),
                position = position_dodge(width = 0.8),
                width = 0.15, linewidth = 0.6) +
  # Add percentage labels
  geom_text(aes(label = percent(Anxiety_Rate, accuracy = 0.1)),
            position = position_dodge(width = 0.8),
            vjust = -0.35, size = 4) +
  scale_fill_manual(values = c("Pre_Pandemic (2017-19)" = COL_PRE,
                               "Pandemic (2021-22)" = COL_POST),
                    name = "Time Period") +
  scale_y_continuous(labels = percent_format(), limits = c(0, NA)) +
  labs(
    title = "Gender Differences in Anxiety Symptoms, Pre vs During Pandemic",
    subtitle = "NHIS sample adult weights; 95% confidence intervals shown",
    x = "Gender",
    y = "Prevalence of High Anxiety"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 13),
    plot.subtitle = element_text(color = "grey40", size = 11),
    legend.position = "top",
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  )
```

# Regression Analysis

## Anxiety

```{r}

# Model 1: Demographics
logit <- feglm(High_Anxiety ~ Pandemic_Era + AGE + SEX + Race_Ethnicity, 
               data = filtered_data, 
               family = binomial(link = "logit"), 
               weights = filtered_data$SAMPWEIGHT,
               vcov = "hetero")

# Model 2: + Baseline SES (Educ)
logit_educ <- feglm(High_Anxiety ~ Pandemic_Era + AGE + SEX + Race_Ethnicity +
                        Education_levels, 
                    data = filtered_data, 
                    family = binomial(link = "logit"), 
                    weights = filtered_data$SAMPWEIGHT,
                    vcov = "hetero")

# Model 3: + Economic Mechanism (SNAP)
logit_full <- feglm(High_Anxiety ~ Pandemic_Era + AGE + SEX + Race_Ethnicity +
                        Education_levels + Received_SNAP, 
                    data = filtered_data, 
                    family = binomial(link = "logit"), 
                    weights = filtered_data$SAMPWEIGHT,
                    vcov = "hetero")

# Regression table
etable(logit, logit_educ, logit_full, 
       headers = c("Base", "+Educ", "+SNAP"),
       digits = 3,
       title = "Impact of Pandemic on Anxiety (Logit Coefficients)"
       ) 

# AME Calculation
ame_logit <- avg_slopes(logit, variables = "Pandemic_Era")
ame_logit_educ <- avg_slopes(logit_educ, variables = "Pandemic_Era")
ame_logit_full <- avg_slopes(logit_full, variables = "Pandemic_Era")

# AME table
modelsummary(
  list(
    "Base" = ame_logit, 
    "+Educ" = ame_logit_educ, 
    "+SNAP" = ame_logit_full),
  estimate = "{estimate} [{conf.low}, {conf.high}]", 
  statistic = NULL,
  gof_omit = ".*",
  title = "Average Marginal Effects of Pandemic Era on Anxiety Probability"
)
```

## Depression

```{r}
# Model 1: Baseline (Demographics only)
logit_dep <- feglm(High_Depression ~ Pandemic_Era + AGE + SEX + Race_Ethnicity, 
                   data = filtered_data, 
                   family = binomial(link = "logit"), 
                   weights = filtered_data$SAMPWEIGHT,
                   vcov = "hetero"
                   )

# Model 2: + Baseline SES (Education)
logit_dep_educ <- feglm(High_Depression ~ Pandemic_Era + AGE + SEX + Race_Ethnicity +
                            Education_levels, 
                        data = filtered_data, 
                        family = binomial(link = "logit"), 
                        weights = filtered_data$SAMPWEIGHT,
                        vcov = "hetero"
                        )

# Model 3: + Economic Mechanism (SNAP)
logit_dep_full <- feglm(High_Depression ~ Pandemic_Era + AGE + SEX + Race_Ethnicity +
                            Education_levels + Received_SNAP, 
                        data = filtered_data, 
                        family = binomial(link = "logit"), 
                        weights = filtered_data$SAMPWEIGHT,
                        vcov = "hetero"
                        )

# Regression Table
etable(logit_dep, logit_dep_educ, logit_dep_full, 
       headers = c("Base", "+Educ", "+SNAP"),
       digits = 3,  
       title = "Impact of Pandemic on Depression (Logit Coefficients)")

# AME
ame_dep_base <- avg_slopes(logit_dep, variables = "Pandemic_Era")
ame_dep_educ <- avg_slopes(logit_dep_educ, variables = "Pandemic_Era")
ame_dep_full <- avg_slopes(logit_dep_full, variables = "Pandemic_Era")

modelsummary(
  list(
    "Base Model" = ame_dep_base, 
    "Control for Educ" = ame_dep_educ, 
    "Control for SNAP" = ame_dep_full
  ),
  estimate = "{estimate} [{conf.low}, {conf.high}]", 
  statistic = NULL, 
  fmt = 3,
  gof_omit = ".*",
  title = "Average Marginal Effects of Pandemic Era on Depression Probability"
)
```
